### 2018-01-14 paper.tex
Rearranging bibliography entries so that citations appear in numerical order
Moved "box 1" to right after rule 1, as requested
Fixed minor typo; added SC & PH URLs (Happy to be reverted.. maybe we removed URLs for reason)

The authors have many years of experience with community-developed lessons
in the context of research computing in the sciences and humanities,
through organizations like Software Carpentry and Programming Historian.
Software Carpentry was founded in 1998 to teach scientists basic computing skills,
and has since spawned two sibling organizations called Data Carpentry and Library Carpentry.
Programming Historian was founded in 2008,
and has evolved into a collaboratively-edited site providing lessons to humanities scholars.
Their guiding principles are that lessons should be:

@@

\begin{mdframed}
\noindent
\textbf{Fig 2. Collaborative open lesson development.} Following the decision to develop 
lessons, activities focus on lesson development as well as community building. 
Boxes surrounded by dotten lines represent community contributions to lessons.
Dashed arrows represent connections to activities outside the original lesson design.
The box enclosed in a dash-dotted line represents unaffiliated learning resources.
\end{mdframed}

>>>>

The authors have many years of experience with community-developed lessons
in the context of research computing in the sciences and humanities,
through organizations like Software Carpentry (\url{https://software-carpentry.org/}) and Programming Historian (\url{https://programminghistorian.org/}).
Software Carpentry was founded in 1998 to teach scientists basic computing skills,
and has since spawned two sibling organizations called Data Carpentry and Library Carpentry.
Programming Historian was founded in 2008,
and has evolved into a collaboratively-edited site providing lessons to humanities scholars.
Their guiding principles are that lessons should be:

@@

\begin{mdframed}
\noindent
\textbf{Fig 2. Collaborative open lesson development.} Following the decision to develop 
lessons, activities focus on lesson development as well as community building. 
Boxes surrounded by dotted lines represent community contributions to lessons.
Dashed arrows represent connections to activities outside the original lesson design.
The box enclosed in a dash-dotted line represents unaffiliated learning resources.
\end{mdframed}
